### 2015-06-05 text/ms.Rmd
Integrate results into abstract

# Includes: mean_sim, mean_ram, slope_sim, auc_sim

@@

# auc_sim has the following list elements:
# > names(auc_sim)
# "mach_range" "ind_range"

# Many elements contain a numeric vector of length 2 indicating lower and 
# upper values.

# Insert one, with, for example: `r auc_sim$mach_range[1]`.
```

@@

What can we do when multiple ecological models give different impressions of
population status? Any single model is unlikely to perform best across all
species, exploitation dynamics, and statuses. Ensemble methods from the fields
of machine learning and climate science provide a powerful tool to optimally
leverage the information contained in multiple ecological models. Here we
evaluate the potential for ensemble methods to improve estimates of fish
population status. We fit four data-limited models of population and
exploitation dynamics and combine their estimates of the mean and slope of
\bbmsy\\ (biomass at maximum sustainable yield) with four ensemble models:
a simple average, a linear model, and two machine learning methods: random
forests and boosted regression trees. We build our ensemble models on a fully
factorial simulated dataset of 5760 fish stocks and test our models on
a cross-validated version of this dataset and on a global database of 166
assessed fish stocks. We find that ensemble models substantially improve
estimates of population status, trajectory, and classification. Machine
learning ensemble models performed the best (XX--XX% improved accuracy, XX--XX%
improved correlation, XX-XX% reduced bias compared to the individual models).
When the same ensembles were applied to a separate dataset of global fish
stocks and compared to status from full stock assessments, ensemble methods
still improved estimates of status and trajectory over individual models
(accuracy, correlation, and bias improved up to XX%, XX%, and XX%). Ensemble
models have great potential to improve estimates of population status and
trajectory across many taxa beyond fish. However, ensemble methods must be
carefully tested, formed from a diverse set of accurate models, and built on
a dataset sufficiently representative of the populations they are applied to.

>>>>

# Includes: mean_sim, mean_ram, slope_sim, auc_sim, ram_stocks_n

@@

# auc_sim has the following list elements:
# > names(auc_sim)
# "mach_range" "ind_range" 
```

@@

What can we do when multiple ecological models give different impressions of population status? Any single model is unlikely to perform best across all species, exploitation dynamics, and statuses. Ensemble methods from the fields climate science and machine learning provide a powerful tool to optimally leverage the information contained in multiple ecological models. Here we evaluate the potential for ensemble methods to improve estimates of fish population status. We fit four data-limited models of population and exploitation dynamics and combine their estimates of the mean and slope of biomass at maximum sustainable yield (\bbmsy\\) with four ensemble models: a simple average, a linear model, and two machine learning methods---random forests and boosted regression trees. We build our ensemble models on a fully factorial simulated dataset of 5760 fish stocks and test our models on a cross-validated version of this dataset and a global database of `r ram_stocks_n` assessed fish stocks. We find that ensemble models substantially improve estimates of population status and trajectory. Machine learning ensemble models performed the best: `r mean_sim$mach_vs_ind_mare_fold`% improved accuracy (reduction in median absolute proportional error), rank-order correlation improved from `r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and bias (median proportional error) declined from `r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. We found similar improvements in performance when predicting the slope of status. When the same simulation-trained ensemble models were applied to a separate dataset of global fish stocks and compared to mean status from data-rich stock assessments, the best ensembles still improved all dimensions of performance (accuracy, correlation, and bias) over the next best individual model. Ensemble models have great potential to improve estimates of population status and trajectory across many taxa beyond fish. However, ensemble methods must be carefully tested, formed from a diverse set of accurate models, and built on a dataset sufficiently representative of the populations they are applied to.
